What We Eval in the Shadows

### 2021-04-15 paper/main.tex
format

\documentclass[review,screen,acmsmall,anonymous=true]{acmart}
%\documentclass[noacm,review,screen,acmsmall,anonymous=true]{acmart}
%Option noacm above messes with the line numbers in review mode
\settopmatter{printfolios=true,printccs=true,printacmref=true}

@@

\section{Background and Previous work}

@@

\begin{lstlisting}
 eval <- function(e, envir = parent.frame(),
                   encl = if(is.list(envir)) parent.frame() else baseenv()) ...
\end{lstlisting}
The most general is \eval. Parameter \c e is the \c{expression} to evaluate,
\c{envir} is the evaluation environment, and \c{encl} is used to look up
variables not found in \c{envir}. The default value of the latter is either the
caller's environment or the base environment.\footnote{It contains all the standard operators and functions in R.} \Eval can take several types for \c e, for
our purposes on the \c{expression}. These can be thought of as the abstract
syntax trees returned by the parser. An \c{expression} can be obtained by
calling \c{quote} or \c{parse} with a string:
\begin{lstlisting}
 > quote(a + b)
 # a + b
 > parse(text="a+b")
 # expression(a+b)
\end{lstlisting}
Usually, expressions are obtained from promises using \c{substitute}. Consider a
function called with \c{x = a+b}, then \c f returns an expression object.
\begin{lstlisting}
 > f <- function(x) substitute(x)
 > f(a+b)
 # expression(a+b)
 > substitute(a+b,list(a=1,b=2))
 # 1+2
\end{lstlisting}
The call to \c{substitute(x)} extracts the unevaluated expression from the
promise \c x. Function \c{substitute(e,envir)} takes two arguments, the second
is used to substitute free variables in \c e.
\begin{lstlisting}
 > environment()
 # <environment: R_GlobalEnv>
\end{lstlisting}
The \c{environment} function returns the current environment. Environments nest,
each has a parent. When creating a new environment with \c{new.env}, the parent
is the current environment. Environment chains can be traversed with
\c{parent.env}, until \c{emptyenv} is reached. The top-level environment is
\c{.GlobalEnv}, it has parents that represent the packages that have been
loaded. One can also directly read, modify or create new bindings, given any
environment:
\begin{itemize}
\item \c{envir\$v} and \c{get("v",envir=envir)}: read  \c{v} from \c{envir};
\item \c{envir\$v<-2} and \c{assign("v",2,envir=envir)}: store 2 in \c{v}, if
  not found, \c{v} is created in \c{envir}.
\end{itemize}
\noindent Environments are used as hash maps as they have reference semantics
and a built-in string look up. Functions \c{parent.frame} and \c{sys.frame}
return environments further up the call stack.
 \begin{lstlisting}
  evalq <- function(e,envir,encl) eval(quote(e),envir,encl)
  eval.parent <- function(e,n) eval(e,parent.frame(n))
  local <- function(e,envir,encl) evalq(e,new.env())
\end{lstlisting}
The three variants can be expressed with \eval: \c{evalq} quotes its
argument to prevent evaluation in the current environment,
\c{eval.parent(e,n)} evaluates \c{e} in the environment of the {\tt n}-th
caller of this function; finally, \c{local} evaluates \c{e} in a new environment
to avoid polluting the current one.

>>>>

\documentclass[review,screen,acmsmall,anonymous=true]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}
\setcopyright{none}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

@@

\newpage
\section{Background and Previous work}

@@

\begin{lstlisting}
 eval <- function(e, envir = parent.frame(),
                   encl = if(is.list(envir)) parent.frame() else baseenv()) ...
\end{lstlisting}
The most general is \eval. Parameter \c e is the \c{expression} to evaluate,
\c{envir} is the evaluation environment, and \c{encl} is used to look up
variables not found in \c{envir}. The default value of the latter is either the
caller's environment or the base environment \Eval can take several types for \c e, for
our purposes on the \c{expression}. These can be thought of as the abstract
syntax trees returned by the parser. An \c{expression} can be obtained by
calling \c{quote} or \c{parse} with a string:
\begin{lstlisting}
 > quote(a + b)
 # a + b
 > parse(text="a+b")
 # expression(a+b)
\end{lstlisting}
Usually, expressions are obtained from promises using \c{substitute}. Consider a
function called with \c{x = a+b}, then \c f returns an expression object.
\begin{lstlisting}
 > f <- function(x) substitute(x)
 > f(a+b)
 # expression(a+b)
 > substitute(a+b,list(a=1,b=2))
 # 1+2
\end{lstlisting}
The call to \c{substitute(x)} extracts the unevaluated expression from the
promise \c x. Function \c{substitute(e,envir)} takes two arguments, the second
is used to substitute free variables in \c e.
\begin{lstlisting}
 > environment()
 # <environment: R_GlobalEnv>
\end{lstlisting}
The \c{environment} function returns the current environment. Environments nest,
each has a parent. When creating a new environment with \c{new.env}, the parent
is the current environment. Environment chains can be traversed with
\c{parent.env}, until \c{emptyenv} is reached. The top-level environment is
\c{.GlobalEnv}, it has parents that represent the packages that have been
loaded. One can also directly read, modify or create new bindings, given any
environment:
\begin{itemize}
\item \c{envir\$v} and \c{get("v",envir=envir)}: read  \c{v} from \c{envir};
\item \c{envir\$v<-2} and \c{assign("v",2,envir=envir)}: store 2 in \c{v}, if
  not found, \c{v} is created in \c{envir}.
\end{itemize}
\noindent Environments are used as hash maps as they have reference semantics
and a built-in string look up. Functions \c{parent.frame} and \c{sys.frame}
return environments further up the call stack.
 \begin{lstlisting}
  evalq <- function(e,envir,encl) eval(quote(e),envir,encl)
  eval.parent <- function(e,n) eval(e,parent.frame(n))
  local <- function(e,envir,encl) evalq(e,new.env())
\end{lstlisting}
The three variants can be expressed with \eval: \c{evalq} quotes its
argument to prevent evaluation in the current environment,
\c{eval.parent(e,n)} evaluates \c{e} in the environment of the {\tt n}-th
caller of this function; finally, \c{local} evaluates \c{e} in a new environment
to avoid polluting the current one.
